Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-10-15 STAT-paper-template/APA/fertile.Rnw
close #16; #17

\end{enumerate}
Most shims are quite simple and look something like what is shown below for \func{read\_csv}.

<<>>=
fertile::read_csv
@

@@

One of the challenges with ensuring that work is reproducible is the issue of dependencies. Many data analysis projects reference a variety of \R packages in their code. When such projects are shared with other users who may not have the required packages downloaded, it can cause errors that prevent the project from running properly.

>>>>

\end{enumerate}
Most shims are quite simple and look something like what is shown below for \textcolor{blue}{\func{read.csv}}.

<<>>=
fertile::read.csv
@

@@

One of the challenges with ensuring that work is reproducible is \textcolor{blue}{\st{the issue of}} dependencies. Many data analysis projects reference a variety of \R packages in their code. When such projects are shared with other users who may not have the required packages downloaded, it can cause errors that prevent the project from running properly.

### 2020-10-15 STAT-paper-template/APA/fertile.tex
close #16; #17

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Compiling... -------------------------------------------------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Rendering R scripts... ---------------------------------------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Running reproducibility checks -------------------------------------- fertile 0.0.0.9028 --}}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Summary of fertile checks ------------------------------------------- fertile 0.0.0.9028 --}}\end{kframe}
\begin{kframe}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Analysis of reproducibility for project\_miceps ---------------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Packages referenced in source code -------------------------------- fertile 0.0.0.9028 --}}\begin{verbatim}
## # A tibble: 9 x 3
##   package       N used_in                    
##   <chr>     <int> <chr>                      
## 1 broom         1 project_miceps/analysis.Rmd
## 2 dplyr         1 project_miceps/analysis.Rmd
## 3 ggplot2       1 project_miceps/analysis.Rmd
## 4 purrr         1 project_miceps/analysis.Rmd
## 5 readr         1 project_miceps/analysis.Rmd
## 6 rmarkdown     1 project_miceps/analysis.Rmd
## 7 skimr         1 project_miceps/analysis.Rmd
## 8 stargazer     1 project_miceps/analysis.Rmd
## 9 tidyr         1 project_miceps/analysis.Rmd
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Files present in directory ---------------------------------------- fertile 0.0.0.9028 --}}\begin{verbatim}
## # A tibble: 9 x 4
##   file               ext        size mime                                       
##   <fs::path>         <chr> <fs::byt> <chr>                                      
## 1 Estrogen_Receptor~ docx     10.97K application/vnd.openxmlformats-officedocum~
## 2 citrate_v_time.png png     188.68K image/png                                  
## 3 proteins_v_time.p~ png     379.22K image/png                                  
## 4 Blot_data_updated~ csv      14.43K text/csv                                   
## 5 CS_data_redone.csv csv       7.39K text/csv                                   
## 6 mice.csv           csv      14.33K text/csv                                   
## 7 README.md          md           39 text/markdown                              
## 8 miceps.Rproj       Rproj       204 text/rstudio                               
## 9 analysis.Rmd       Rmd       4.94K text/x-markdown
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Suggestions for moving files -------------------------------------- fertile 0.0.0.9028 --}}\begin{verbatim}
## # A tibble: 7 x 3
##   path_rel           dir_rel    cmd                                             
##   <fs::path>         <fs::path> <chr>                                           
## 1 Blot_data_updated~ data-raw   file_move('project_miceps/Blot_data_updated.csv~
## 2 CS_data_redone.csv data-raw   file_move('project_miceps/CS_data_redone.csv', ~
## 3 Estrogen_Receptor~ inst/other file_move('project_miceps/Estrogen_Receptors.do~
## 4 analysis.Rmd       vignettes  file_move('project_miceps/analysis.Rmd', fs::di~
## 5 citrate_v_time.png inst/image file_move('project_miceps/citrate_v_time.png', ~
## 6 mice.csv           data-raw   file_move('project_miceps/mice.csv', fs::dir_cr~
## 7 proteins_v_time.p~ inst/image file_move('project_miceps/proteins_v_time.png',~
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Problematic paths logged ------------------------------------------ fertile 0.0.0.9028 --}}\begin{verbatim}
## NULL
\end{verbatim}
\end{kframe}
\end{knitrout}

\textcolor{blue}{Both the proactive and retroactive features available in \pkg{fertile} are enabled automatically upon the loading of the package. To prevent users from accidentally enabling or disabling features, \pkg{fertile} does not provide any option to control which features are active. However, those who want to use the proactive features can simply  refrain from using the retroactive-specific functions.
Conversely, those who want to use only the retroactive features can wait to load \pkg{fertile} until they are ready to produce a report on their project.}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{log_report}\hlstd{()}
\end{alltt}
\begin{verbatim}
## # A tibble: 5 x 4
##   path         path_abs                             func     timestamp          
##   <chr>        <chr>                                <chr>    <dttm>             
## 1 package:pur~ <NA>                                 base::l~ 2020-10-14 18:12:20
## 2 package:for~ <NA>                                 base::l~ 2020-10-14 18:12:20
## 3 Seed Before  <NA>                                 20       2020-10-14 18:12:20
## 4 project_mic~ /Users/audreybertin/Documents/ferti~ readr::~ 2020-10-14 18:12:20
## 5 Seed After   <NA>                                 34       2020-10-14 18:12:20
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fertile}\hlopt{::}\hlstd{read.csv}
\end{alltt}
\begin{verbatim}
## function(file, ...) {
##   if (interactive_log_on()) {
##     log_push(file, "utils::read.csv")
##     check_path_safe(file, ... = "utils::read.csv")
##     utils::read.csv(file, ...)
##   }
## }
## <bytecode: 0x7fc7f433c548>
## <environment: namespace:fertile>
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir}
\end{alltt}
\begin{verbatim}
## [1] "project_miceps"
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(proj_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## project_miceps/Blot_data_updated.csv   project_miceps/CS_data_redone.csv      
## project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\begin{alltt}
\hlstd{temp_dir} \hlkwb{<-} \hlkwd{sandbox}\hlstd{(proj_dir)}
\hlstd{temp_dir}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpyKNgZn/project_miceps
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(temp_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpyKNgZn/project_miceps/Blot_data_updated.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpyKNgZn/project_miceps/CS_data_redone.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpyKNgZn/project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Compiling... ------------------------------------------------------------------------------------------------------------------ fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Rendering R scripts... -------------------------------------------------------------------------------------------------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Running reproducibility checks ------------------------------------------------------------------------------------------------ fertile 0.0.0.9028 --}}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Summary of fertile checks ----------------------------------------------------------------------------------------------------- fertile 0.0.0.9028 --}}\end{kframe}
\begin{kframe}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Analysis of reproducibility for project\_miceps -------------------------------------------------------------------------------- fertile 0.0.0.9028 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Packages referenced in source code ------------------------------------------------------------------------------------------ fertile 0.0.0.9028 --}}\begin{verbatim}
## # A tibble: 9 x 3
##   package       N used_in                    
##   <chr>     <int> <chr>                      
## 1 broom         1 project_miceps/analysis.Rmd
## 2 dplyr         1 project_miceps/analysis.Rmd
## 3 ggplot2       1 project_miceps/analysis.Rmd
## 4 purrr         1 project_miceps/analysis.Rmd
## 5 readr         1 project_miceps/analysis.Rmd
## 6 rmarkdown     1 project_miceps/analysis.Rmd
## 7 skimr         1 project_miceps/analysis.Rmd
## 8 stargazer     1 project_miceps/analysis.Rmd
## 9 tidyr         1 project_miceps/analysis.Rmd
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Files present in directory -------------------------------------------------------------------------------------------------- fertile 0.0.0.9028 --}}\begin{verbatim}
## # A tibble: 9 x 4
##   file               ext        size mime                                       
##   <fs::path>         <chr> <fs::byt> <chr>                                      
## 1 Estrogen_Receptor~ docx     10.97K application/vnd.openxmlformats-officedocum~
## 2 citrate_v_time.png png     188.29K image/png                                  
## 3 proteins_v_time.p~ png     377.95K image/png                                  
## 4 Blot_data_updated~ csv      14.43K text/csv                                   
## 5 CS_data_redone.csv csv       7.39K text/csv                                   
## 6 mice.csv           csv      14.33K text/csv                                   
## 7 README.md          md           39 text/markdown                              
## 8 miceps.Rproj       Rproj       204 text/rstudio                               
## 9 analysis.Rmd       Rmd       4.94K text/x-markdown
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Suggestions for moving files ------------------------------------------------------------------------------------------------ fertile 0.0.0.9028 --}}\begin{verbatim}
## # A tibble: 7 x 3
##   path_rel           dir_rel    cmd                                             
##   <fs::path>         <fs::path> <chr>                                           
## 1 Blot_data_updated~ data-raw   file_move('project_miceps/Blot_data_updated.csv~
## 2 CS_data_redone.csv data-raw   file_move('project_miceps/CS_data_redone.csv', ~
## 3 Estrogen_Receptor~ inst/other file_move('project_miceps/Estrogen_Receptors.do~
## 4 analysis.Rmd       vignettes  file_move('project_miceps/analysis.Rmd', fs::di~
## 5 citrate_v_time.png inst/image file_move('project_miceps/citrate_v_time.png', ~
## 6 mice.csv           data-raw   file_move('project_miceps/mice.csv', fs::dir_cr~
## 7 proteins_v_time.p~ inst/image file_move('project_miceps/proteins_v_time.png',~
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Problematic paths logged ---------------------------------------------------------------------------------------------------- fertile 0.0.0.9028 --}}\begin{verbatim}
## NULL
\end{verbatim}
\end{kframe}
\end{knitrout}

\textcolor{blue}{Both the proactive and retroactive features available in \pkg{fertile} are enabled automatically upon loading the package. To prevent users from accidentally enabling or disabling features, \pkg{fertile} does not provide any option to control which features are active. However, those who want to use the proactive features can simply  refrain from using the retroactive-specific functions.
Conversely, those who want to use only the retroactive features can wait to load \pkg{fertile} until they are ready to produce a report on their project.}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{log_report}\hlstd{()}
\end{alltt}
\begin{verbatim}
## # A tibble: 5 x 4
##   path         path_abs                             func     timestamp          
##   <chr>        <chr>                                <chr>    <dttm>             
## 1 package:pur~ <NA>                                 base::l~ 2020-10-15 17:20:28
## 2 package:for~ <NA>                                 base::l~ 2020-10-15 17:20:28
## 3 Seed Before  <NA>                                 20       2020-10-15 17:20:28
## 4 project_mic~ /home/bbaumer/Dropbox/git/fertile-p~ readr::~ 2020-10-15 17:20:28
## 5 Seed After   <NA>                                 35       2020-10-15 17:20:28
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fertile}\hlopt{::}\hlstd{read.csv}
\end{alltt}
\begin{verbatim}
## function(file, ...) {
##   if (interactive_log_on()) {
##     log_push(file, "utils::read.csv")
##     check_path_safe(file, ... = "utils::read.csv")
##     utils::read.csv(file, ...)
##   }
## }
## <bytecode: 0x55e884da4358>
## <environment: namespace:fertile>
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir}
\end{alltt}
\begin{verbatim}
## [1] "project_miceps"
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(proj_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## project_miceps/Blot_data_updated.csv   project_miceps/CS_data_redone.csv      
## project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\begin{alltt}
\hlstd{temp_dir} \hlkwb{<-} \hlkwd{sandbox}\hlstd{(proj_dir)}
\hlstd{temp_dir}
\end{alltt}
\begin{verbatim}
## /tmp/RtmpqsLI66/project_miceps
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(temp_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## /tmp/RtmpqsLI66/project_miceps/Blot_data_updated.csv
## /tmp/RtmpqsLI66/project_miceps/CS_data_redone.csv
## /tmp/RtmpqsLI66/project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\end{kframe}
\end{knitrout}
